### 2019-05-23 reviews/response.md

We thank the reviewers for their detailed and insightful feedback.

We have added three new implementations to Task Bench: Dask,
MPI+OpenMP and MPI+CUDA. Results are included in the evaluation
section, including preliminary results from experiments with GPUs on
the Piz Daint supercomputer.

@@

Major changes in the revised paper:

  * New implementations: Dask, MPI+OpenMP and MPI+CUDA
  * New sections
      - Implementation: sections 4.3 (Dask) and 4.5 (MPI+X)
      - Evaluation: sections 5.6 (weak/strong scaling) and 5.9 (GPUs)
  * New figures
      - Listings 1 and 2 (code samples)
      - Figures 11, 12, 15 (experiments)

### 2019-05-23 1_introduction.tex
Tweak text.

To address the first issue, we present Task Bench, a
\emph{parameterized} benchmark designed for exploring the performance
behaviors of parallel and distributed programming systems under a
variety of conditions. A critical property of Task Bench is that,
while able to express a wide variety of typical parallel programming
patterns, it is simple enough to be implemented with reasonable effort
to a level of quality sufficient for comparative studies.

>>>>

To address the first issue, we present Task Bench, a
\emph{parameterized} benchmark designed for exploring the performance
behaviors of parallel and distributed programming systems under a
variety of conditions. A critical property of Task Bench is that,
while able to express a wide variety of typical parallel programming
patterns, it is simple enough to be implemented with reasonable effort
to a level of quality sufficient for comparative
studies. Task Bench is provides a core API that is shared across the
various system implementations. New benchmarks created with Task Bench
immediately run on all systems, and new systems immediately run all
benchmarks. Thus, Task Bench is much more productive for benchmarking
a wide range of phenomena than the standard approach in which each
benchmark must be implemented separately for each system.
